Appendix

### 2018-06-12 figures/06_k.Rmd
adjust k viz to make lws and nws more comparable

k_viz_iws <- ggplot(
  fit_df_iws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
    geom_density_ridges(size = 0.1, scale = 1) + 
    scale_fill_manual(values = c("grey", 
                            rep(c(viridis::viridis(1, begin = 0.5), 
                                  viridis::viridis(1, begin = 0)), 7))) +
    scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 7))) +
    cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                     axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                     axis.line.x = element_line(size = 1, 
                                     colour = "black"),
                                     axis.line.y = element_line(size = 1, 
                                                       colour = "black"), 
                                     legend.position = "none", 
                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
  xlab("Coefficient Value") + ylab("") + 
  scale_y_discrete(breaks = levels(fit_df_iws$key)[
    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
                   labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

@@

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, scale = 1) + 
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("Coefficient Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

@@

plot_grid(
  k_viz_iws + ggtitle("A. LWS scale") + xlim(0.8, 1.6),
  k_viz_nws + ggtitle("B. NWS scale") + xlim(0.8, 1.6), 
  ncol = 2, align = "v", rel_widths = c(1, 1)) + 
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))

>>>>

k_viz_iws <- ggplot(
  fit_df_iws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
    geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
    geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
    scale_fill_manual(values = c("grey", 
                            rep(c(viridis::viridis(1, begin = 0.5), 
                                  viridis::viridis(1, begin = 0)), 7))) +
    scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 7))) +
    cowplot::theme_cowplot() + theme(panel.grid.major.y = element_blank(),
                                     axis.text = element_text(size = 10),
                                     axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                     axis.line.x = element_line(size = 1, 
                                     colour = "black"),
                                     axis.line.y = element_line(size = 1, 
                                                       colour = "black"), 
                                     legend.position = "none", 
                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
  xlab("Coefficient Value") + ylab("") + 
  scale_y_discrete(breaks = levels(fit_df_iws$key)[
    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
                   labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

@@

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
  geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("Coefficient Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

@@

plot_grid(
  k_viz_iws + ggtitle("Lake Watershed") + xlim(0.8, 1.6),
  k_viz_nws + ggtitle("Network Watershed") + xlim(0.8, 1.6), 
  ncol = 2, align = "v", rel_widths = c(1, 1)) + 
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))

### 2018-06-12 manuscript/appendix.Rmd
adjust k viz to make lws and nws more comparable

iws_outline <- concaveman(st_cast(iws, "POINT"))
nws_outline <- concaveman(st_cast(nws, "POINT"))

ggplot() + 
  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
  geom_sf(data = nws) +
  geom_sf(data = nws_lakes[1,], color = "cyan") +
  geom_sf(data = nws_lakes[2,], color = "yellow") +
  coord_sf(crs = st_crs(nws), datum = NA) + 
  # geom_sf(data = iws) + 
  theme_void()

@@

@@

# palette <- c("black",
#               "black")

@@

save_tmap(m_nes, "../figures/best_partition_maps-1.png",
          scale = 0.7, width = 3.125)
```

>>>>

iws_outline <- concaveman(st_cast(iws, "POINT"))
nws_outline <- concaveman(st_cast(nws, "POINT"))
lake_1_outline <- concaveman(st_cast(nws_lakes[1,], "POINT"))
lake_2_outline <- concaveman(st_cast(nws_lakes[2,], "POINT"))

ggplot() + 
  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
  geom_sf(data = nws) +
  geom_sf(data = lake_1_outline, color = "cyan") +
  geom_sf(data = lake_2_outline, color = "yellow") +
  coord_sf(crs = st_crs(nws), datum = NA) + 
  # geom_sf(data = iws) + 
  theme_void()

@@

palette <- c("black",
              "black")

m_nes <-  tm_shape(us) + tm_polygons() +
          tm_shape(nes_extent) + tm_borders(lwd = 3) +
          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
                                 size = 0.2, legend.show = FALSE, 
                                 title = "Average Link Length") +
          # tm_credits("National Eutrophication Survey") +
          tm_layout(frame = FALSE,
                    legend.outside = FALSE,
                    legend.stack = "horizontal")

save_tmap(m_nes, "../figures/best_partition_maps-1.png",
          scale = 0.7, width = 3.125)

# # # # #

@@

@@

save_tmap(m_nes, "../figures/best_partition_maps-2.png",
          scale = 0.7, width = 3.125)
```
